Kate chronic samples

### 2019-11-26 scripts/03_lefse_CR_tox.Rmd
remove the special features when doing renorm

```{r}
# input: relative abundance unstratified for pathway abundance
relab <- read_tsv('../data/humann2_res/humann2_final_out/humann2_pathabundance_cpm_unstratified.tsv') %>% 
  rename(sampleid = names(.)[1]) %>% 
  rename_all(funs(str_replace(., '_Abundance$',''))) %>% 
  # remove the unmapped and the unintegrated record
  filter(!sampleid %in% c('UNMAPPED','UNINTEGRATED'))

>>>>

```{r}
# input: relative abundance unstratified for pathway abundance
relab <- read_tsv('../data/humann2_res/humann2_final_out/humann2_pathabundance_cpm_unstratified.tsv') %>% 
  rename(sampleid = names(.)[1]) %>% 
  rename_all(funs(str_replace(., '_Abundance$','')))

### 2019-11-26 scripts/z01_kate_sample_sort.Rmd
remove the special features when doing renorm

@@

target_have %>% 
  group_by(period, case_status) %>% 
  summarise(cnt = n())

# how many need to be uploaded (35)
target %>% 
  filter(!sampleid %in% current$sampleid) %>% 
  select(directory) %>% 
  mutate(cmd = str_glue('rsync --progress --partial -avz {directory} daia1@lilac.mskcc.org:~/my_workdir/samples/kate')) %>% 
  ungroup() %>%
  select(cmd) %>%  
  write_csv('../data/upload_kate_43.sh', col_names = F)
```

>>>>

### Select the target samples that go into this comparison

@@

# how many need to be uploaded 
target %>% 
  filter(!sampleid %in% current$sampleid) %>% 
  select(directory) %>% 
  mutate(cmd = str_glue('rsync --progress --partial -avz {directory} daia1@lilac.mskcc.org:~/my_workdir/samples/kate')) %>% 
  ungroup() %>%
  select(cmd) %>%   
  write_csv('../data/upload_kate_43.sh', col_names = F)
```

### Create the pheno table and make sure the input two tables are correctly sorted

```{r}
pheno <- target  %>% 
  ungroup %>% 
  mutate(fid = str_extract(directory, 'Sample.+IGO'),
         fid = str_replace(fid, 'Sample_',''),
         fid = str_replace(fid, '_IGO',''))  %>% 
  select(sampleid, case_status, fid)

# the cts table 
cts <- read_tsv('../data/kate/pwabun/humann2_final_out/humann2_pathabundance_cpm_unstratified.tsv') %>% 
  rename(sampleid = names(.)[1]) %>% 
  rename_all(funs(str_replace(., '_Abundance$',''))) 
cts <- bind_cols(cts[,1],cts[,pheno$fid])

cts %>% 
  write_tsv('../data/kate/input_lefse_cts.tsv')

pheno_col <- pheno %>% 
  select(case_status) %>% 
  t %>% 
  write.table('../data/kate/input_lefse_pheno.txt', sep = '\t', quote = F, row.names = T, col.names = F)
